|

### 2017-11-23 boettiger-eddelbuettel.Rmd
Flush out a bit more about singularity
include example of importing and running rocker container on singularity, as reviewer 1 suggests.

Deploying Docker containers on centrally administrated multi-user machines, such
as department or university clusters, has previously been more difficult, since
system adminstrators do not want to allow the elevated user permissions the Docker
runtime environment requires.  To work around this problem, Lawrence Berkeley National
Labs (LBNL) has made 'Singularity' \citep{singularity}: a container runtime environment that users can
both install and use to run most Docker containers without requiring root privileges,
making it easier to deploy Rocker containers in this context as well.

@@

>>>>

@@

## HPC application

The portability of Rocker images can be particularly valuable in High Performance Computing
contexts Setting up a specific R environment on High Performance Computing platforms and other 
centrally administrated multi-user machines or clusters has traditionally been challenging
due to restrictions on root access that may be needed to install certain libraries. 
Versions of R and packages installed by the system administrator may also lag behind
the most recent releases. Deploying Docker containers on HPC systems has previously
been more very problematic since most
system adminstrators do not want to allow the elevated user permissions the Docker
runtime environment requires.  To work around this problem, Lawrence Berkeley National
Labs (LBNL) has made 'Singularity' \citep{singularity}: a container runtime environment that users can
both install and use to run most Docker containers without requiring root privileges. 
Singularity has seen rapid adoption in the HPC community (<http://singularity.lbl.gov/install-request>).
Rocker containers can be run through Singularity with a single command much like
the native Docker commands, _e.g._

```
singularity exec docker://rocker/tidyverse:latest R
```

More details can be found in the Singularity documentation.
